Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-14 Report/ieee_journal.tex
Updated with rohit comments
updated minor changes

\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}

@@

\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\toggletrue{single_column}
\togglefalse{enable_dist_fig}

@@

\begin{IEEEkeywords}
\acs{MIMO}-\acs{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
\end{IEEEkeywords}

\acresetall
\section{Introduction} \label{sec-1}
\input{introduction}

>>>>

\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}

@@

\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\togglefalse{single_column}
\togglefalse{enable_dist_fig}

@@

\begin{IEEEkeywords}
\ac{MIMO}-\ac{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
\end{IEEEkeywords}

\acresetall

\section{Introduction} \label{sec-1}
\input{introduction}

### 2014-10-14 Report/kkt_mse_approach.tex
updated minor changes

The problem in \eqref{kkt-mse-1} is solved using the\ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables as shown in the Appendix \ref{a-1}. Upon solving, we obtain the iterative solution as

@@

\subsubsection*{Convergence}
The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}. The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}. Once the dual variables are converged or iterated to a certain accuracy, the receivers are updated using the \ac{MMSE} objective. In this algorithm, when \me{t_k > Q_k}, \me{\sigma_{l,k,n}} will be zero (dual feasibility), thereby reducing the priority weights \me{\alpha_{l,k,n}} present in the transmit precoder expression in \eqref{kkt-mse-4.3}.

>>>>

The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables as shown in the Appendix \ref{a-1}. Upon solving, we obtain the iterative solution as

@@

\subsubsection*{Convergence}
The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}. The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive beamformers \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}. Once the dual variables are converged or iterated for certain accuracy, the receivers are updated using the \ac{MMSE} objective. Since the \ac{MMSE} receiver is optimal for the fixed transmit precoders, the objective function will improve or stays the same after the receiver update leading to a monotonic convergence of the iterative algorithm provided in \eqref{kkt-mse-4}.
